\begin{thebibliography}{9}
\addcontentsline{toc}{section}{References}

\bibitem{boid0}
\textit{Reynolds, C.W. (1987) Flocks, Herds and Schools: A Distributed Behavioral Model. ACM Siggraph Computer Graphics, 21, 25-34.}

\bibitem{boid1}
Craig W. Reynolds,\\
\textit{“Boids (Flocks, Herds, and Schools: A Distributed Behavioral
Model).” Red3d.com, 2019, www.red3d.com/cwr/boids/.}

\bibitem{boid2}
Bajec, I. Lebar, et al.\\
The computational beauty of flocking: boids revisited
\textit{“The Computational Beauty of Flocking: Boids Revisited.” Mathematical and Computer Modelling of Dynamical Systems, vol. 13, no. 4, Aug. 2007, pp. 331–347, 10.1080/13873950600883485. Accessed 15 June 2021.}

\bibitem{boid3}
A.V. Moere,\\
Time-Varying Data Visualization Using Information Flocking Boids,\hfill\\
\textit{  " IEEE Symposium on Information Visualization, 2004, pp. 97-104, doi: 10.1109/INFVIS.2004.65.}

\bibitem{boid4}
Craig W. Reynolds
Steering Behaviors For Autonomous Characters
\textit{Www.red3d.com, www.red3d.com/cwr/steer/gdc99/}

 \bibitem{mult1} Qu, Guannan. “Scalable Multi-Agent Reinforcement Learning for Networked Systems with Average Reward.” 
 
 \bibitem{shaping}
 Adam Daniel Laud
Theory and Application of Reward Shaping in Reinforcement learning

%DroneCompanies
\bibitem{com1}
Drone Up,\\
\textit{“Let’s Fly! | DroneUp.” www.droneup.com/.} 

\bibitem{com2}
Wing,\\
Owned by Google,\\
\textit{Wing. wing.com/.}

\bibitem{com3}
“DHL Drone Delivery and Parcelcopter Technology\\
\textit{Discover DHL.” Dhl.com, 2022, \\ www.dhl.com/discover/en-my/business/business-ethics//parcelcopter-drone-technology.\hfill}

\bibitem{com4}
Skyopener Project.\\
\textit{M3 Systems, m3systems.eu/en/skyopener-project/. Accessed 16 Apr. 2022.} 

%Drone efficiency
\bibitem{eff1}
Kirschstein, Thomas. \\
\textit{“Comparison of Energy Demands of Drone-Based and Ground-Based Parcel Delivery Services.” Transportation Research Part D: Transport and Environment, vol. 78, 1 Jan. 2020, p. 102209, www.sciencedirect.com/science/article/pii/S1361920919309575, 10.1016/j.trd.2019.102209. Accessed 17 Mar. 2020.} 

\bibitem{eff2}
Gulden, Timothy R.\\
The Energy Implications of Drones for Package Delivery,\\ 
\textit{The Energy Implications of Drones for Package Delivery: A Geographic Information System Comparison. Santa Monica, CA: RAND Corporation, 2017.}

%Drone Restricted Zones
\bibitem{res1}
NO FLY DRONES\\
\textit{“No Fly Drones.” No Fly Drones, www.noflydrones.co.uk/.} 

%Drone Range
\bibitem{far1}
NEXTECH\\
\textit{“VTOL Vertical Take off and Landing Drone.” Nextechnology,\\ shop.airbornedrones.co/products/vtol-drone. Accessed 16 Apr. 2022.}

\bibitem{far2}
DJI\\
\textit{“Mavic 3 - Specs - DJI.” DJI Official, www.dji.com/uk/mavic-3/specs.} 

%Drone Terrorism
\bibitem{ter1}
ASSOCIATION OF THE UNITED STATES ARMY\\
\textit{“The Role of Drones in Future Terrorist Attacks.” AUSA, 26 Feb. 2021,\\ www.ausa.org/publications/role-drones-future-terrorist-attacks.} 

\bibitem{ter2}
Yaacoub, Jean-Paul, and Ola Salman.\\
 “Security Analysis of Drones Systems: Attacks, Limitations, and Recommendations.”\\
\textit{Internet of Things, May 2020, p. 100218,\\ www.ncbi.nlm.nih.gov/pmc/articles/PMC7206421/, 10.1016/j.iot.2020.100218.}

\bibitem{ter3}
D-fend\\
\textit{“Drone Threat, Counter Drone.” D-Fend Solutions,\\ www.d-fendsolutions.com/drone-threat-overview/. Accessed 16 Apr. 2022.}

\bibitem{ter4}
Seongjoon Park et al.\\
\textit{Park, Seongjoon, et al. “Survey on Anti-Drone Systems: Components, Designs, and Challenges.” IEEE Access, vol. 9, 2021, pp. 42635–42659, 10.1109/access.2021.3065926.}

%Flocking
\bibitem{flo1}
Chao Yan et al.\\
\textit{Yan, Chao, et al. “Fixed-Wing UAVs Flocking in Continuous Spaces: A Deep Reinforcement Learning Approach.” Robotics and Autonomous Systems, vol. 131, Sept. 2020, p. 103594, 10.1016/j.robot.2020.103594.}
%Neural networks and actor critic
\bibitem{neu1}
Understanding Actor Critic Methods and A2C\\
\textit{Yoon, Chris. “Understanding Actor Critic Methods.” Medium, 17 July 2019,\\ towardsdatascience.com/understanding-actor-critic-methods-931b97b6df3f.},

\bibitem{neu2}
Deriving Policy Gradients and Implementing REINFORCE\\
\textit{Yoon, Chris. “Deriving Policy Gradients and Implementing REINFORCE.” Medium, 23 May 2019, medium.com/@thechrisyoon/deriving-policy-gradients-and-implementing-reinforce-f887949bd63.},

%Perceptron
\bibitem{per1}
Perceptron,\\
Brilliant Math \& Science Wiki.”\\
\textit{“ Brilliant.org, brilliant.org/wiki/perceptron/\#:~:text=The\%20perceptron\%20is\%20a\%20machine.}
%Deep learning
\bibitem{deep1}
Charu C. Aggarwal,\\
\textit{Machine Learning with Shallow Neural Networks. In: Neural Networks and Deep Learning. Springer, Cham.},
(2018).

\bibitem{deep2}
Deep Learning and the Game of Go\\
\textit{Pumperla, Max, and Kevin Ferguson. Deep Learning and the Game of Go. Shelter Island, Ny, Manning Publications Co, 2019.}

%Reinforcement learning
\bibitem{rl1}
Sutton, Richard S,\\
\textit{ and Andrew Barto. Reinforcement Learning : An Introduction. Cambridge, Ma ; Lodon, The Mit Press, 2018.}

\bibitem{rl2}
Grondman, Ivo, et al.\\
\textit{ “A Survey of Actor-Critic Reinforcement Learning: Standard and Natural Policy Gradients.” IEEE Transactions on Systems, Man, and Cybernetics, Part c (Applications and Reviews), vol. 42, no. 6, Nov. 2012, pp. 1291–1307, 10.1109/tsmcc.2012.2218595. Accessed 27 Feb. 2020.}

\bibitem{rl3}
“Create MATLAB Reinforcement Learning Environments - MATLAB \& Simulink.”\\
\textit{www.mathworks.com/help/reinforcement-learning/ug/create-matlab-environments-for-reinforcement-learning.html.\hfill}
%Control
\bibitem{con1}
Stengel, Robert F.\\
Optimal Control and Estimation.\\
\textit{ Google Books, Courier Corporation, 20 Sept. 1994,\\ books.google.co.uk/books?hl=en\&lr=\&id=byRgDwAAQBAJ\&oi=fnd\&pg=PA1\&dq=Stengel\\+Optimal+Control+and+Estimation. Accessed 16 Apr. 2022.}

\bibitem{con2}
Control Systems/Controllability and Observability,\\
Wikibooks, Open Books for an Open World.” \\
\textit{En.wikibooks.org, en.wikibooks.org/wiki/Control\_Systems/Controllability\_and\_Observability\\\#:~:text=The\%20concept\%20of\%20controllability\%20refers.}

%Example visualisations
\bibitem{ex1}
“Boids Algorithm.\\
\textit{” Eater.net, eater.net/boids.},

%Code Help
\bibitem{cod1}
“The Nature of Code.”\\
\textit{ Natureofcode.com, natureofcode.com/book/chapter-6-autonomous-agents/.}

\bibitem{cod2}
“The Nature of Code.”\\
\textit{ Natureofcode.com, natureofcode.com/.}

\bibitem{mon1}
Metropolis, Nicholas, and S. Ulam.\\
\textit{ “The Monte Carlo Method.” Journal of the American Statistical Association, vol. 44, no. 247, Sept. 1949, pp. 335–341, 10.1080/01621459.1949.10483310.}

\bibitem{mar1}
Littman, M. L.\\
“Markov Decision Processes.”\\
\textit{ ScienceDirect, Pergamon, 1 Jan. 2001,\\ www.sciencedirect.com/science/article/pii/B0080430767006148.}

\bibitem{ac1}
Fujimoto, Scott, et al.\\
\textit{Addressing Function Approximation Error in Actor-Critic Methods.}


\bibitem{ac2}
Silver, David, et al.\\
\textit{ Deterministic Policy Gradient Algorithms.}

\bibitem{bel1}
TORRES.AI, Jordi.\\
“The Bellman Equation.”\\
The Bellman Equation\\
\textit{ Medium, 15 June 2020, towardsdatascience.com/the-bellman-equation-59258a0d3fa7.}


\bibitem{bel2}
\textit{“Bellman Optimality Equation in Reinforcement Learning.” Analytics Vidhya, 13 Feb. 2021, www.analyticsvidhya.com/blog/2021/02/understanding-the-bellman-optimality-equation-in-reinforcement-learning/\#:~:text=The\%20Optimal\%20Value\%20Function\%20is. Accessed 16 Apr. 2022.}

\bibitem{td1}
Hood, Jordan J.\\
“Reinforcement Learning: Temporal Difference (TD) Learning.”\\
\textit{www.lancaster.ac.uk/stor-i-student-sites/jordan-j-hood/2021/04/12/reinforcement-learning-temporal-difference-td-learning/.}

\bibitem{mul1}
Deshpande, Paresh, et al.\\
Formation Control of Multi-Agent Systems with Double Integrator Dynamics Using Delayed Static Output Feedback.”\\
\textit{ “ IEEE Xplore, 1 Dec. 2011, ieeexplore.ieee.org/document/6161074/figures\#figures. Accessed 16 Apr. 2022.}

\bibitem{rew1}
Brummerloh, Daniel.\\
“Ultimate Guide for AI Game Creation Part 2 — Training.”\\
\textit{ Medium, 7 Jan. 2021, towardsdatascience.com/ultimate-guide-for-ai-game-creation-part-2-training-e252108dfbd1. Accessed 16 Apr. 2022.}


\bibitem{mtl1}
“Create MATLAB Reinforcement Learning Environments - MATLAB \& Simulink.”\\
\textit{ Www.mathworks.com, www.mathworks.com/help/reinforcement-learning/ug/create-matlab-environments-for-reinforcement-learning.html. Accessed 16 Apr. 2022.}

\bibitem{cat1}
Cahill, Andy. \\
“Catastrophic Forgetting in Reinforcement-Learning Environments.”\\
\textit{ Ourarchive.otago.ac.nz, 2011, ourarchive.otago.ac.nz/handle/10523/1765. Accessed 16 Apr. 2022.}

\bibitem{lex1}
Fridman, Lex.\\
“MIT Deep Learning Basics: Introduction and Overview.”\\
\textit{ YouTube, 11 Jan. 2019, www.youtube.com/watch?v=O5xeyoRL95U.}

\bibitem{quad1}
“Dynamics Modeling of a Highly-Maneuverable Fixed-Wing UAV.”\\
\textit{ Researchgate, Apr. 2013, www.researchgate.net/publication/264773227\_Dynamics\_Modeling\_of\_a\_Highly-Maneuverable\_Fixed-Wing\_UAV.}

\bibitem{fix1}
“Accurate Simulator for Motion of the Quadcopter; Assuming Dynamic and Aerodynamic Effects.”\\
\textit{ Esearchgate, Apr. 2019, www.researchgate.net/publication/332980824\_Accurate\_Simulator\_for\_Motion\_of\_the\_Quadcopter\_Assuming\_Dynamic\_and\_Aerodynamic\_Effects.}

\bibitem{ref1}
Yin, Xiang, et al.\\
“Quadtree Representation \& Compression of Spatial Data.”\\
\textit{ Www.semanticscholar.org,\\ www.semanticscholar.org/paper/Quadtree-Representation-\%26-Compression-of-Spatial-Yin-Diintsch/d45d7f7d8817170ee0f9cec2db083a4852848621?p2df.}

\bibitem{ref2}
Shiri, Aidin, et al.\\
“Energy-Efficient Hardware for Language Guided Reinforcement Learning.”\\
\textit{ Proceedings of the 2020 on Great Lakes Symposium on VLSI, 7 Sept. 2020, eehpc.csee.umbc.edu/publications/pdf/2020/2020\_GLSVLSI\_RL\_Structured\_Language.pdf, 10.1145/3386263.3407652. Accessed 16 Apr. 2022.}

 \bibitem{AI}
 https://openai.com/api/
 
  \bibitem{MPE}
 Huichu Zhang Shanghai Jiao Tong University Shanghai, et al. “CityFlow: A Multi-Agent Reinforcement Learning Environment for Large Scale City Traffic Scenario: The World Wide Web Conference.” ACM Other Conferences, 1 May 2019, https://dl.acm.org/doi/abs/10.1145/3308558.3314139?casa\_token=nbe2mKJTQcEAAAAA\%3AJsYLiuBcf2e-DQ4YFfC0WLX0CRlDuj1UJnyeUpdcFouJDvfeosKk64t08rUAfQKStvFnwPB0Ieg. 
\end{thebibliography}
\clearpage % start appendices on a new page